\chapter{Actions}
This section will list all the actions that are usable in the Starcraft environment.

\section{Attack action}
\begin{tabularx}{\textwidth}{lX}
 Description & Attack the given enemy unit. \\
 Syntax & \verb|attack(<TargetID>)| \\
 Parameters & \verb|<TargetID>|: The \textit{ID} of the target that will be attacked.\\
 Pre & The targeted unit is attack capable. \\
 Post &  The targeted unit is being attacked by your unit.
\end{tabularx}

\section{Move action}
\begin{tabularx}{\textwidth}{lX}
 Description & Move to the chosen location. \\
 Syntax & \verb|move(<X>,<Y>)| \\
 Parameters & \verb|<X>|: The x-coordinate of the chosen location \\
            &  \verb|<Y>|: The y-coordinate of the chosen location \\
 Pre & The unit is capable of moving to the chosen location. \\
 Post & The unit moves to the chosen location (ignoring any other unit it might pass by).
\end{tabularx}

\section{Attack move action}
\begin{tabularx}{\textwidth}{lX}
 Description & Go to the given location and attack everything you encounter. \\
 Syntax & \verb|attack(<X>,<Y>)| \\
 Parameters & \verb|<X>|: The x-coordinate of the chosen location \\
            & \verb|<Y>|: The y-coordinate of the chosen location \\
 Pre & The unit is capable of moving to the chosen location. \\
 Post & The unit moves to the chosen locations and attacks any attack capable enemy unit it encounters.
\end{tabularx}

\section{Upgrade action}
\begin{tabularx}{\textwidth}{lX}
 Description & Starts working on the chosen upgrade. \\
 Syntax & \verb|upgrade(<UpgradeName>)| \\
 Parameters & \verb|<UpgradeName>|: The name of the upgrade you want to upgrade.\\
 Pre & The unit is capable of upgrading and has sufficient resources to do so. \\
 Post & The unit starts upgrading the chosen upgrade.
\end{tabularx}

\section{Build action}
\begin{tabularx}{\textwidth}{lX}
 Desription & Build a building on the given location. \\
 Syntax & \verb|build(<Type>,<X>,<Y>)| \\
 Parameters & \verb|<Type>|: The Type of the building that has to be built.\\
            & \verb|<X>|: The x-coordinate of the chosen build location \\
            & \verb|<Y>|: The y-coordinate of the chosen build location \\
 Pre & The unit is capable of constructing the chosen building and the chosen location is not obstructed. \\
 Post & The unit starts constructing the chosen building at the chosen location.
\end{tabularx}

\section{Gather action}
\begin{tabularx}{\textwidth}{lX}
 Description & Gather the chosen resource (minerals or vespene gas). \\
 Syntax & \verb|gather(<ID>)| \\
 Parameters & \verb|<ID>|: The \textit{ID} of the chosen resource. \\
 Pre & The unit is capable of performing the gather action and a valid resource unit is selected. \\
 Post & The unit starts gathering the chosen resource.
\end{tabularx}

\section{Train action}
\begin{tabularx}{\textwidth}{lX}
 Description & Train the chosen unit. \\
 Syntax & \verb|train(<Type>)| \\
 Parameters & \verb|<Type>|: The type of unit to train.\\
 Pre & The production facility is capable of producing the chosen unit and has sufficient resources to do so. \\
 Post & The production facility starts producing the chosen unit.
\end{tabularx}

\section{Stop action}
\begin{tabularx}{\textwidth}{lX}
 Description & Stop performing the current action. \\
 Syntax & \verb|stop| \\
 Pre & The unit is performing some kind of action. \\
 Post & The unit stops performing the action.
\end{tabularx}

\section{Ability action}
\begin{tabularx}{\textwidth}{lX}
 Description & Use an (researched) ability. \\
 Syntax & \verb|ability(<Type>)| \\
 Parameters & \verb|<Type>|: The type of technology to use.\\
 Pre & The chosen tech type is researched and the unit is capable of performing the chosen tech type. \\
 Post & The unit performs the chosen tech ability.
\end{tabularx}

\section{Ability on target action}
\begin{tabularx}{\textwidth}{lX}
 Description & Use an (researched) ability on a target. \\
 Syntax & \verb|ability(<Type>, <Target>)| \\
 Parameters & \verb|<Type>|: The type of technology to use.\\
            & \verb|<Target>|: The target to use the technology on.\\
 Pre & The chosen tech type is researched, the unit is capable of performing the chosen tech type and the chosen target is attack capable. \\
 Post & The unit performs the chosen tech ability on the chosen target.
\end{tabularx}

\section{Ability on location action}
\begin{tabularx}{\textwidth}{lX}
 Description & use an (researched) ability on a location. \\
 Syntax & \verb|ability(<Type>, <X>, <Y>)| \\
 Parameters & \verb|<Type>|: The type of technology to use.\\
            & \verb|<X>|: The x-coordinate of the chosen location \\
            & \verb|<Y>|: The y-coordinate of the chosen location. \\
 Pre & The chosen tech type is researched, the unit is capable of performing the chosen tech type and the chosen location is valid to perform an action on. \\
 Post & The unit performs the chosen tech ability on the chosen location.
\end{tabularx}

\section{Research action}
\begin{tabularx}{\textwidth}{lX}
 Description & Research a chosen tech type. \\
 Syntax & \verb|research(<Type>)| \\
 Parameters & \verb|<Type>|: The type of tech to research.\\
 Pre & The building is capable of researching the chosen tech type and has sufficient resources to do so. \\
 Post & The building starts researching the chosen tech type.
\end{tabularx}

\section{Set rally point action}
\begin{tabularx}{\textwidth}{lX}
 Description & Set the rally point on a specific location. When the rally point is set, produced units of this production facility will automatically move to this location. \\
 Syntax & \verb|setRallyPoint(<X>, <Y>)| \\
 Parameters & \verb|<X>|: The x-coordinate of the chosen rally location \\
            & \verb|<Y>|: The y-coordinate of the chosen rally location. \\
 Pre & The building is capable of setting up a rally point and the chosen location is a valid location where units can move to. \\
 Post & The building sets the rally point on the chosen location.
\end{tabularx}

\section{Set rally point to unit action}
\begin{tabularx}{\textwidth}{lX}
 Description & Set the rally point on a unit. When the rally point is set, produced units of this production facility will automatically move to this unit. \\
 Syntax & \verb|setRallyPoint(<Unit>)| \\
 Parameters & \verb|<Unit>|: The unit to set the rally point on.\\
 Pre & The building is capable of setting up a rally point and the chosen unit is on a valid location where units can move to. \\
 Post & The building sets the rally point on the chosen unit.
\end{tabularx}

\section{Lift action}
\begin{tabularx}{\textwidth}{lX}
 Description & Lift into the air. \\
 Syntax & \verb|lift| \\
 Pre & The building is capable of flying and is not busy performing any other action. \\
 Post & The building starts flying. \\
 Note & Only for Terran buildings.
\end{tabularx}

\section{Land action}
\begin{tabularx}{\textwidth}{lX}
 Desription & Land on the given location. \\
 Syntax & \verb|land(<X>, <Y>)| \\
 Parameters & \verb|<X>|: The x-coordinate of the chosen land location \\
            & \verb|<Y>|: The y-coordinate of the chosen land location. \\
 Pre & The unit is currently flying and is capable of landing on the chosen location. \\
 Post & The unit lands on the chosen location. \\
 Note & The location has to be visible.
\end{tabularx}

\section{Build addon action}
\begin{tabularx}{\textwidth}{lX}
 Desription & Build the chosen addon. \\
 Syntax & \verb|buildAddon(<Name>)| \\
 Parameters & \verb|<Name>|: The name of the chosen addon.\\
 Pre & The building is capable of building the addon and does not already have the addon. \\
 Post & The building starts constructing the addon. \\
 Note & Only for Terran buildings.
\end{tabularx}

\section{Load action}
\begin{tabularx}{\textwidth}{lX}
 Desription & Load a unit. \\
 Syntax & \verb|load(<ID>)| \\
 Parameters & \verb|<ID>|: The \textit{ID} of the unit to load into this (loadable) unit.\\
 Pre & The unit is capable of loading other units inside it and still has enough space prodivded for the targeted unit. \\
 Post & The targeted unit starts walking to the loadable unit and loads into it.
\end{tabularx}

\section{Unload action}
\begin{tabularx}{\textwidth}{lX}
 Desription & Unload an unit. \\
 Syntax & \verb|unload(<ID>)| \\
 Parameters & \verb|<ID>|: The \textit{ID} of the unit to unload from this (loadable) unit.\\
 Pre & The unit is capable of loading other units inside it. \\
 Post & The targeted unit is unloaded and stands next to the (loadable) unit.
\end{tabularx}

\section{Unload all action}
\begin{tabularx}{\textwidth}{lX}
 Desription & Unload all units. \\
 Syntax & \verb|unloadAll| \\
 Pre & The unit is capable of loading other units inside it. \\
 Post & All units are unloaded and stand next to the (loadable) unit.
\end{tabularx}

\section{Cancel action}
\begin{tabularx}{\textwidth}{lX}
 Desription & Cancel the construction of the unit. \\
 Syntax & \verb|cancel| \\
 Pre & The unit is morphing, beingConstructed, researching or upgrading. \\
 Post & The morphing, construction, upgrading or researching is cancelled.
\end{tabularx}

\section{Patrol action}
\begin{tabularx}{\textwidth}{lX}
 Desription & Patrol an unit between the place it's standing and the given location. \\
 Syntax & \verb|patrol(<X>, <Y>)| \\
 Parameters & \verb|<X>|: The x-coordinate of the chosen location \\
            &  \verb|<Y>|: The y-coordinate of the chosen location \\
 Pre & The unit is capable of moving to the chosen location. \\
 Post & The unit patrols between the chosen location (ignoring any other unit it might pass by) and the location it was originally standing.
\end{tabularx}

%Kweet niet of ik deze action wil houden
%\section{RightClick action}
%\begin{tabularx}{\textwidth}{lX}
 %Desription & Right clicks on a unit. (This is action should not be necessary but could be used for testing %purposes) \\
 %Syntax & rightClick(<ID>) or rightClick(<X>,<Y>) \\
 %Parameters & <ID>: The ID of a unit.\\
 %           & <X>,<Y>: A position.\\
 %Effects &  The unit rightclicks
%\end{tabularx}