\chapter{TechTypes}
\label{techtype}
Here is the list of all tech types that can be researched. 

\section{Terran Units}
These are all the Terran tech types.

\subsection{Battle Cruisers}
These are the tech type(s) for Battle Cruiser units. \\
\verb|Yamato Gun|

\subsection{Command Centers}
These are the tech type(s) for Command Center units. \\
\verb|Scanner Sweep| 

\subsection{Ghosts}
These are the tech type(s) for Ghost units. \\
\verb|Lockdown| \\
\verb|Personel Cloaking| \\
\verb|Nuclear Strike|

\subsection{Marines and Firebats}
These are the tech type(s) for Marine and Firebat units. \\
\verb|Stim Packs|

\subsection{Medics}
These are the tech type(s) for Medic units. \\
\verb|Healing| \\
\verb|Restoration| \\
\verb|Optical Flare|

\subsection{Science Vessels}
These are the tech type(s) for Science Vessel units. \\
\verb|Defensive Matrix| \\
\verb|EMP Shockwave| \\
\verb|Irradiate| 

\subsection{Siege Tanks}
These are the tech type(s) for Siege Tank units. \\
\verb|Tank Siege Mode| 

\subsection{Vultures}
These are the tech type(s) for Vulture units. \\
\verb|Spider Mines|

\subsection{Wraith}
These are the tech type(s) for Wraith units. \\
\verb|Cloaking Field| 

\section{Protoss Units}
These are all the Protoss tech types.

\subsection{Arbiters}
These are the tech type(s) for Arbiter units. \\
\verb|Cloaking Field| \\
\verb|Recall| \\
\verb|Stasis Field|

\subsection{Corsairs}
These are the tech type(s) for Corsair units. \\
\verb|Disruption Web|

\subsection{Dark Archons}
These are the tech type(s) for Dark Archon units. \\
\verb|Feedback| \\
\verb|Maelstrom| \\
\verb|Mind Control|

\subsection{Dark Templars}
These are the tech type(s) for Dark Templar units. \\
\verb|Dark Archon Meld|

\subsection{High Templars}
These are the tech type(s) for High Templar units. \\
\verb|Archon Warp| \\
\verb|Psionic Storm| \\
\verb|Hallucination|

\section{Zerg Units}
These are all the Zerg tech types.

\subsection{Generic}
These are the tech type(s) which all ground units can use. \\
\verb|Burrowing| \\

\subsection{Defilers}
These are the tech type(s) for Defilers units. \\
\verb|Dark Swarm| \\
\verb|Plague| \\
\verb|Consume| 

\subsection{Hydralisks}
These are the tech type(s) for Hydralisk units. \\
\verb|Lurker Aspect|

\subsection{Lurkers}
These are the tech type(s) for Lurker units. \\ 
\verb|Burrowing| (Can be used without having it researched)

\subsection{Queens}
These are the tech type(s) for Queen units. \\ 
\verb|Infestation| \\
\verb|Parasite| \\
\verb|Ensnare| \\
\verb|Spawn Broodlings| \\