\chapter{Unit Types}
\label{unittype}
Here is the list of all unit types you can specify within the mas2g. Note that when you bind your agent to a specific unit type in the mas2g, the first letter of the name unit type should always be non-capital!

\section{Terran Units}
These are all the terran unit types.

\subsection{Terran Ground Units}
These are all the terran ground units.
\\\\
\verb|Terran Firebat| \\
\verb|Terran Ghost| \\
\verb|Terran Goliath| \\
\verb|Terran Marine| \\
\verb|Terran Medic| \\
\verb|Terran SCV| \\
\verb|Terran Siege Tank| \\
\verb|Terran Vulture| \\
\verb|Terran Vulture Spider Mine| \\


\subsection{Terran Air Units}
These are all the terran air units.
\\\\
\verb|Terran Battlecruiser| \\
\verb|Terran Dropship| \\
\verb|Terran Science Vessel| \\
\verb|Terran Valkyrie| \\
\verb|Terran Wraith| \\

\subsection{Terran Building Units}
These are all the terran building units.
\\\\
\verb|Terran Academy| \\
\verb|Terran Armory| \\
\verb|Terran Barracks| \\
\verb|Terran Bunker| \\
\verb|Terran Command Center| \\
\verb|Terran Engineering Bay| \\
\verb|Terran Factory| \\
\verb|Terran Missle Turret| \\
\verb|Terran Refinery| \\
\verb|Terran Science Facility| \\
\verb|Terran Starport| \\
\verb|Terran Supply Depot| \\

\subsection{Terran Addons}
These are all the terran addon units. Note that terran is the only race capable of making addons.
\\\\
\verb|Terran Comsat Station| \\
\verb|Terran Control Tower| \\
\verb|Terran Covert Ops| \\
\verb|Terran Machine Shop| \\
\verb|Terran Nuclear Silo| \\
\verb|Terran Physics Lab| \\

\section{Protoss Units}
These are all the protoss unit types.

\subsection{Protoss Ground Units}
These are all the protoss ground units.
\\\\
\verb|Protoss Archon| \\
\verb|Protoss Dark Archon| \\
\verb|Protoss Dark Templar| \\
\verb|Protoss Dragoon| \\
\verb|Protoss High Templar| \\
\verb|Protoss Probe| \\
\verb|Protoss Reaver| \\
\verb|Protoss Scarab| \\
\verb|Protoss Zealot| \\

\subsection{Protoss Air Units}
These are all the protoss air units.
\\\\
\verb|Protoss Arbiter| \\
\verb|Protoss Carrier| \\
\verb|Protoss Corsair| \\
\verb|Protoss Interceptor| \\
\verb|Protoss Observer| \\
\verb|Protoss Scout| \\
\verb|Protoss Shuttle| \\

\subsection{Protoss Building Units}
These are all the protoss building units.
\\\\
\verb|Protoss Arbiter Tribunal| \\
\verb|Protoss Assimilator| \\
\verb|Protoss Citadel of Adun| \\
\verb|Protoss Cybernatics Core| \\
\verb|Protoss Fleet Beacon| \\
\verb|Protoss Forge| \\
\verb|Protoss Gateway| \\
\verb|Protoss Nexus| \\
\verb|Protoss Observatory| \\
\verb|Protoss Photon Cannon| \\
\verb|Protoss Pylon| \\
\verb|Protoss Robotics Facility| \\
\verb|Protoss Robotics Support Bay| \\
\verb|Protoss Shield Battery| \\
\verb|Protoss Stargate| \\
\verb|Protoss Templar Archives| \\

\section{Zerg Units}
These are all the zerg units.

\subsection{Zerg Ground Units}
These are all the zerg ground units.
\\\\
\verb|Zerg Broodling| \\
\verb|Zerg Defiler| \\
\verb|Zerg Drone| \\
\verb|Zerg Egg| \\
\verb|Zerg Hydralisk| \\
\verb|Zerg Infested Terran| \\
\verb|Zerg Larva| \\
\verb|Zerg Lurker| \\
\verb|Zerg Lurker Egg| \\
\verb|Zerg Ultralisk| \\
\verb|Zerg Zergling| \\

\subsection{Zerg Air Units}
These are all the zerg air units.
\\\\
\verb|Zerg Cocoon| \\
\verb|Zerg Devourer| \\
\verb|Zerg Guardian| \\
\verb|Zerg Mutalisk| \\
\verb|Zerg Overlord| \\
\verb|Zerg Queen| \\
\verb|Zerg Scourge| \\

\subsection{Zerg Building Units}
These are all the zerg building units.
\\\\
\verb|Zerg Creep Colony| \\
\verb|Zerg Defiler Mound| \\
\verb|Zerg Evolution Chamber| \\
\verb|Zerg Extractor| \\
\verb|Zerg Greater Spire| \\
\verb|Zerg Hatchery| \\
\verb|Zerg Hive| \\
\verb|Zerg Hydralisk Den| \\
\verb|Zerg Infested Command Center| \\
\verb|Zerg Lair| \\
\verb|Zerg Nydus Canal| \\
\verb|Zerg Queens Nest| \\
\verb|Zerg Spawning Pool| \\
\verb|Zerg Spire| \\
\verb|Zerg Spore Colony| \\
\verb|Zerg Sunken Colony| \\
\verb|Zerg Ultralisk Cavern| \\
