\chapter{UpgradeTypes}
\label{upgradetype}
Here is the list of all upgrade types that can be upgraded. 

\section{Terran Units}
These are all the Terran upgrade types for Terran units. \\

\subsection{Academy}
These are the upgrade type(s) the Academy offers. \\
\verb|U 238 Shells| \\
\verb|Caduceus Reactor|

\subsection{Armory}
These are the upgrade type(s) the Armory offers. \\
\verb|Terran Vehicle Weapons|\\
\verb|Terran Vehicle Plating|\\
\verb|Terran Ship Weapons|\\
\verb|Terran Ship Plating|\\

\subsection{Covert Ops}
These are the upgrade type(s) the Covert Ops offers. \\
\verb|Ocular Implants|\\
\verb|Moebius Reactor|

\subsection{Engineering Bay}
These are the upgrade type(s) the Engineering Bay offers. \\
\verb|Terran Infantry Weapons|\\
\verb|Terran Infantry Armor|\\

\subsection{Machine Shop}
These are the upgrade type(s) the Machine Shop offers. \\
\verb|Ion Thrusters|\\
\verb|Charon Boosters|

\subsection{Physics Lab}
These are the upgrade type(s) the Physics Lab offers. \\
\verb|Colossus Reactor|

\subsection{Science Facility}
These are the upgrade type(s) the Science Facility offers. \\
\verb|Titan Reactor|

\subsection{Control Tower}
These are the upgrade type(s) the Control Tower offers. \\
\verb|Apollo Reactor|

\section{Protoss Units}
These are all the Protoss upgrade types for Protoss units. \\

\subsection{Arbiter Tribunal}
These are the upgrade type(s) the Arbiter Tribunal offers. \\
\verb|Khaydarin Core|

\subsection{Citadel of Adun}
These are the upgrade type(s) the Citadel of Adun offers. \\
\verb|Protoss Plasma Shields|\\
\verb|Leg Enhancements|

\subsection{Cybernetics Core}
These are the upgrade type(s) the Cybernetics Core offers. \\
\verb|Singularity Charge|\\
\verb|Protoss Air Weapons|\\
\verb|Protoss Air Armor|\\

\subsection{Fleet Beacon}
These are the upgrade type(s) the Fleet Beacon offers. \\
\verb|Apial Sensors|\\
\verb|Gravitic Thrusters| \\
\verb|Argus Jewel|\\
\verb|Carrier Capacity|

\subsection{Forge}
These are the upgrade type(s) the Forge offers. \\
\verb|Protoss Plasma Shields|\\
\verb|Protoss Ground Armor|\\
\verb|Protoss Ground Weapons|\\

\subsection{Observatory}
These are the upgrade type(s) the Observatory offers. \\
\verb|Gravitic Boosters|\\
\verb|Sensor Array|

\subsection{Robotics Support Bay}
These are the upgrade type(s) the Robotics Support Bay offers. \\
\verb|Reaver Capacity|\\
\verb|Scarab Damage|\\
\verb|Gravitic Drive|

\subsection{Templar Archives}
These are the upgrade type(s) the Templar Archives offers. \\
\verb|Argus Talisman|\\
\verb|Khaydarin Amulet|

\section{Zerg Units}
These are all the Zerg upgrade types for Zerg units. \\

\subsection{Defiler Mound}
These are the upgrade type(s) the Defiler Mound offers. \\
\verb|Metasynaptic Node|

\subsection{Evolution Chamber}
These are the upgrade type(s) the Evolution Chamber offers. \\
\verb|Zerg Melee Attacks|\\
\verb|Zerg Missile Attacks|\\
\verb|Zerg Carapace|

\subsection{Hydralisk Den}
These are the upgrade type(s) the Hydralisk Den offers. \\
\verb|Muscular Augments|\\
\verb|Grooved Spines|

\subsection{Lair and Hive}
These are the upgrade type(s) the Lair and Hive offers. \\
\verb|Ventral Sacs| \\
\verb|Antennae|\\
\verb|Pneumatized Carapace|

\subsection{Queen's Nest}
These are the upgrade type(s) the Queen's Nest offers. \\
\verb|Gamete Meiosis|

\subsection{Spawning Pool}
These are the upgrade type(s) the Spawning Pool offers. \\
\verb|Metabolic Boost|\\
\verb|Adrenal Glands|

\subsection{(Greater) Spire}
These are the upgrade type(s) the (Greater) Spire offers. \\
\verb|Zerg Flyer Carapace|\\
\verb|Zerg Flyer Attacks|

\subsection{Ultralisk Cavern}
These are the upgrade type(s) the Ultralisk Cavern offers. \\
\verb|Chitinous Plating|\\
\verb|Anabolic Synthesis|